SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-18 Chapters/Chapter02.tex
atom has lost it

>>>>

\begin{enumerate}
  \item Calculate critical distance.ipynb
  \item Calculate radius for any SDM.ipynb
  \item Classification Test 1.ipynb
  \item Classification Test 2.ipynb
  \item Classification Test 3-Copy1.ipynb
  \item Classification Test 3.ipynb
  \item Critical Distance - New.ipynb
  \item Critical Distance.ipynb
  \item Distance between bitstrings.ipynb
  \item Distances of activated hard-locations.ipynb
  \item Generates a new SDM.ipynb
  \item index.rst
  \item Intersection of activated hard-locations.ipynb
  \item Kanerva-Table-7 - Experiment.ipynb
  \item Kanerva-Table-7.3 - Generic Read.ipynb
  \item Kanerva-Table-7.3 - Multiple dimensions.ipynb
  \item Kanerva-Table-7.3 - Weighted table write.ipynb
  \item Kanerva-Table-7.3.ipynb
  \item Kanerva's Figure 1.2.ipynb
  \item Noise filter 2.ipynb
  \item Noise filter A-Z 0-1 Generator.ipynb
  \item Noise filter with labels.ipynb
  \item Noise filter.ipynb
  \item Number of activated hard-locations.ipynb
  \item Performance test.ipynb
  \item Reseting hard-locations.ipynb
  \item Sequences (Kanerva Ch 8).ipynb
  \item Sequences in one SDM (Kanerva Ch 8).ipynb
  \item table74.pickle
  \item TicTacToe - Old (TO BE DELETED).ipynb
  \item TicTacToe.ipynb
  \item tmp-TO-BE-DELETED-2.ipynb
  \item tmp-TO-BE-DELETED.ipynb
  \item Untitled.ipynb
  \item Untitled1.ipynb
  \item Weighted operations using information.ipynb
\end{enumerate}
